Very simplified likelihood

### 2024-09-03 inst/very_simplified_likelihood.Rmd
typos

```{r analuyzelmp,cache=TRUE}
jjf <- function(x){f_vec_arn(x,O$rank,O$n,log=TRUE)}
system.time(optolym <- optimize(jjf, c(0.45,0.5), maximum=TRUE))
```

@@

```{r makeolymplike}
a <- seq(from=0.3,to=0.65,len=45)
L <- f_vec_arn(a,O$rank,O$n,log=TRUE)
Lmax <- jjf(optolym$maximum)
Lmax
L <- L-Lmax
```

@@

segments(x0=a_lower,y0=-1.5,y1=-3.5)
segments(x0=a_upper,y0=-1.5,y1=-3.5)

text(x=a_lower,y=-3,"0.380",pos=4)
text(x=a_upper,y=-3,"0.563",pos=2)
}
plotolymp()
pdf(file="plotolymp.pdf")
plotolymp()
dev.off()
```

>>>>

```{r analyze_athletics_olymp,cache=TRUE}
jjf <- function(x){f_vec_arn(x,O$rank,O$n-1,log=TRUE)}
system.time(optolym <- optimize(jjf, c(0.45,0.65), maximum=TRUE))
```

@@

```{r make_athletic_like}
a <- seq(from=0.35,to=0.65,len=45)
L <- f_vec_arn(a,O$rank,O$n-1,log=TRUE)
Lmax <- jjf(optolym$maximum)
Lmax
L <- L-Lmax
```

@@

segments(x0=a_lower,y0=-1.5,y1=-3.5)
segments(x0=a_upper,y0=-1.5,y1=-3.5)
grid()
text(x=a_lower,y=-3,"0.380",pos=4)
text(x=a_upper,y=-3,"0.563",pos=2)
}
plotolymp()
pdf(file="plotolymp.pdf")
plotolymp()
dev.off()
```
